---
title: "AC.R.Capstone Vignette"
Author: "Andrew S. Clappison"
date: "2019-11-03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AC.R.Capstone Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AC.R.Capstone)
library(tidyverse)
```

## Information About this package

This package was created for Andrew Clappison's Mastering Software Development in R Coursera Course.

## Included Data

Data is included with this package.

National Geophysical Data Center / World Data Service (NGDC/WDS): Significant Earthquake Database. National Geophysical Data Center, NOAA. doi:10.7289/V5TD9V7K

## Example Workflow


1. First clean the data provided in the package:

```{r Clean_Data}
clean_data <- AC.R.Capstone::eq_clean_data(AC.R.Capstone::NOAA_eq_data)
tail(clean_data)
```

Note: eq_clean_data() calls the function eq_location_clean() so the following is not necessary to do, but has been written for completeness:

```{r Clean_Data_2}
example_data <- AC.R.Capstone::eq_location_clean(AC.R.Capstone::NOAA_eq_data)
tail(example_data$LOCATION_NAME)
```

2. To create a timeline plot:

```{r Plot_TimeLines, fig.width = 6, fig.height = 6}
clean_data %>%
  dplyr::filter(COUNTRY %in% c("CANADA", "USA")) %>%
  dplyr::filter(DATE >= lubridate::ymd("2000-01-01")) %>%
  dplyr::filter(DATE <= lubridate::ymd("2010-01-01")) %>%
  ggplot2::ggplot(mapping = ggplot2::aes(x = DATE, y = COUNTRY, size = EQ_PRIMARY)) +
  AC.R.Capstone::geom_timeline(mapping = ggplot2::aes(fill = DEATHS), 
                             alpha = 0.25, xmin = lubridate::ymd("2000-01-01"), xmax = lubridate::ymd("2010-01-01")) +
  AC.R.Capstone::geom_timeline_label(mapping = ggplot2::aes(label = LOCATION_NAME), n_max = 5) +
  AC.R.Capstone::theme_timeline
                             
```

3. To create a map plot:

```{r Plot_Maps, fig.width = 6, fig.height = 6}
clean_data %>%
  dplyr::filter(COUNTRY == "CANADA" & DATE >= lubridate::ymd("2010-01-01")) %>%
  dplyr::mutate(map_label = AC.R.Capstone::eq_create_label(.)) %>%
  AC.R.Capstone::eq_map(annot_col = "map_label") 
```
